Multiple Linear Regression on Sleep Data

### 2025-05-08 paper/paper.qmd
set seed 510 and final LASSO regression model

```{r include=FALSE}
## Split Training/Test Data
sleep_sp <- sleep_test %>% initial_split(prop = 0.8, strata=sleep_duration)
rtrain <- sleep_sp %>% training()
rtest <- sleep_sp %>% testing()

@@

>>>>

```{r include=FALSE}
set.seed(510)

## Split Training/Test Data
sleep_sp <- sleep_test %>% initial_split(prop = 0.8, strata=sleep_duration)
rtrain <- sleep_sp %>% training()
rtest <- sleep_sp %>% testing()

@@

```{r}
sleep_test_final <- sleep_test_vif %>%
  dplyr::select(!c(gender, occupation, bmi_category, sleep_disorder, daily_steps))

model_final <- lm(sleep_duration ~., sleep_test_final)
summary(model_final)
```
